A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-03-10 analysis/article.Rmd
feat: describe model development in methods section

tar_load(tbl1)
tar_load(tbl_observed_vs_expected_mortality)
```

@@

TODO: selected final model, analysis, feature selection

@@

<!-- TODO:
use `pattern` argument to provide "{n} ({p}%)" for categorial/dichotomos
variables after this PR is merged
https://github.com/ddsjoberg/gtsummary/pull/951
-->

>>>>

tar_load(tbl1)
tar_load(tbl_observed_vs_expected_mortality)

tar_load(ameldcfg)
```

@@

After selecting the final model we train and validated it as described in
@harrell1996.
Briefly we develop our model and predict survival at `r ameldcfg$times` days.
The predictions were grouped into equal sized intervals so that there
are `r ameldcfg$m` patients in each interval.
For each group the mean survival probability and the difference to the
Kaplan-Meier estimate was calculated.
The same procedure was repeated for `r ameldcfg$nboot` bootstrap samples.
Subsequently the differences between predicted survival and Kaplan-Meier
estimates of the bootstrap samples were averaged and added to the original
model difference to obtain a bias-corrected estimated between predicted and
observed survival.

The final model was compared against the MELD, MELD-Na and MELD-Plus7 score
using the area under the time-dependent ROC curve (AUC)
based on the nonparametric inverse probability of censoring weighting estimator
(IPCW) [@blanche2013].

@@
